What do incoming university students believe about open science practices in

### 2021-04-01 analysis/Manuscript.Rmd
clean up code

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals

@@

#correlation test with CI and p-values in a clean tibble
critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
tidy(critical_corr_test)

cor(df$`norm rating`, df$`cnorm rating`)

>>>>

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

#correlation test with CI and p-values in a clean tibble
critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
# tidy(critical_corr_test)
